---
knit: (
  function(inputFile, encoding) { 

    title <- 'Demo Word Report'

    rmarkdown::render( 
      input       = inputFile, 
      encoding    = encoding, 
      params      = list(doc_title = title),      
      output_file = paste(title, format(Sys.time(), '%d_%b_%Y'),sep='_')) })
params: 
  doc_title:
    input: text
    label: Title and filename
    value: 'Filled above'
title:  "`r params$doc_title`"
author: "Lisa Avery"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  word_document:
    reference_docx: wordTemplate.docx
    fig_height: 5
    fig_width: 7
  pdf_document:
    fig_height: 5
    fig_width: 7  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning=FALSE,message = FALSE)
library(tidyverse)
library(knitr)
library(reportRx)
library(survival) 
library(xtable)
library(aod)

file_type='word' # or change to anything else for latex/pdf


# function to print table to word
printTable <- function(tab,doc_format='word'){
if (doc_format=='word'){
  for (j in 1:ncol(tab)){
  to_bold = grep('textbf',tab[[j]])  
  tab[[j]] <- gsub('~','&nbsp;',tab[[j]])
  tab[[j]] <- gsub('textbf','',tab[[j]])
  tab[[j]] <- gsub('[\\]','',tab[[j]])
  tab[[j]] <- gsub('[{]','',tab[[j]])
  tab[[j]] <- gsub('[}]','',tab[[j]])
  tab[[j]] <- gsub('[$]','',tab[[j]])
  tab[[j]][to_bold] <- paste0('**',tab[[j]][to_bold],'**')
  }
}
kable(tab, booktabs=F,
      align = paste(c('l',rep('r',ncol(tab)-1)),collapse = '',sep=''))
}

#  redefine petsum if output is to word
if (file_type=='word'){
  orig_function <- petsum
  petsum <- function(data, response, group = 1, times = c(12, 14), units = "months"){
    new.out <- capture.output(orig_function(data, response, group , times , units ))
  new.out <- gsub('textbf','**',new.out)
  new.out <- gsub('[\\]','',new.out)
  new.out <- gsub('[{]','',new.out)
  new.out <- gsub('[}]','**',new.out)
  new.out <- gsub('[*][*][*][*]','',new.out)
 
  for (i in 1:length(new.out)) cat(new.out[[i]],'\n')
  }
}

```

# Rmarkdown
Code is contained in chunks, as with sweave. You can include code chunks with the keyboard shortcut Ctrl + Alt + I (OS X: Cmd + Option + I). Chunk options are similar to sweave:
Many different options to include there, a few relevant ones are:
- **include:** TRUE or FALSE, if FALSE it prevents code and results from appearing in the finished file. R Markdown still runs the code in the chunk, and the results can be used by other chunks 
- **echo**: can take TRUE or FALSE, whether the R code should be printed or not
- **message**: TRUE or FALSE, indicates whether any messages from the code should be printed.
- **results**: character string with one of 'markup', 'asis', 'hold' or 'hide'  
- **warnings**: TRUE or FALSE, indicates whether any warnings from the code should be printed.

# Sample Data

Here is the lung data:
```{r}
str(lung)
```

Make some changes to the variables:
```{r, echo=T}
# lung$Sex <- factor(sapply(lung$sex,function(s){
#   if(s==1) return("Male")
#   if(s==2) return("Female")
# }))
# lung$Sex <- relevel(lung$Sex,ref="Male")
# 
# lung$ECOG <- factor(sapply(lung$ph.ecog,function(s){
#   if( is.na(s)) return(NA)
#   if( s %in% c(0,1) ) return("0-1")
#   if( s %in% c(2,3) ) return("2-3")
# }))
# 
# lung$status_0_1 <- ifelse(lung$status==2,1,0)

# In the tidyverse
lung <- lung %>%
  mutate(
    Sex = relevel(factor(if_else(sex==1,'Male','Female')),ref = 'Male'),
    ECOG = factor(case_when(
      ph.ecog %in% c(1,0) ~'0-1',
      ph.ecog %in% c(2,3) ~'2-3'
    )),
    status_0_1 =if_else(lung$status==2,1,0)
  )
```

# Results

## Tables

Table 1 for males vs females
```{r}
tbl1<-covsum(data = lung, covs = c('age','ECOG','meal.cal','wt.loss'), maincov = "Sex")

printTable(tbl1)
```


Specify the test for continuous and categorical variable separately. Default options are 'rank-sum' and 'Chi-squared' test for continuous and categorical, respectively. I also added a flag to display interquantile ranges as opposed to min and max in summarizing continuous variables.

```{r cat-and-continuous}
tbl2 <- covsum(data =lung, covs = c('age','ECOG','meal.cal','wt.loss'), maincov = "Sex",
        IQR = TRUE, testcont = "ANOVA", testcat = "Fisher")
printTable(tbl2)
```


Combining Tables
```{r}
t1 = covsum(data = lung, covs = c('age','meal.cal','wt.loss'), maincov = "Sex")

t2 = covsum(data = lung, covs = c('ECOG'), maincov = "Sex", testcat = "Fisher")

printTable(rbind(t1,t2))
```


## Summarizing regression models
There are two ways in which we can summarize regression models: (1) one variable at a time and (2) under a multivariable model.

Currently, the supported regression models are: "linear", "logistic", "coxph", "crr", and "boxcox". If option "type" is not provided, the function will try to guess the model based on the outcome provided.

### Univariable
Logistic
```{r}
tblLM <- uvsum(response = "status_0_1", covs = c('Sex', 'age','ECOG','meal.cal','wt.loss'), data = lung)
printTable(tblLM)
```



Cox PH
```{r}
tblPH <- uvsum(response = c("time","status_0_1"), covs = c('Sex','age','ECOG','meal.cal','wt.loss'), data = lung)
printTable(tblPH)
```

### Multivariable

Logistic
```{r}
log_fit <- glm(status_0_1 ~ Sex + ECOG + meal.cal + wt.loss, data = lung, family=binomial)
printTable( mvsum(model = log_fit, data = lung))
```


Logistic with interaction
```{r}
log_fit1 <- glm(status_0_1 ~ Sex*meal.cal + age + ECOG + wt.loss, data = lung, family=binomial)
printTable(mvsum(model = log_fit1, data = lung))

```


Cox PH with interaction
```{r}
cox_fit1 <- coxph(Surv(time,status_0_1) ~ Sex*meal.cal + age + ECOG + wt.loss, data = lung)
printTable(mvsum(model = cox_fit1, data = lung))

```

## KM plots
```{r ungrouped-km}
plotkm(data = lung, response = c("time","status_0_1"), group = 1, 
       pos = "bottomleft", units = "days", CI = F, legend = T, title = "")

```

```{r grouped-km}
plotkm(data = lung, response = c("time","status_0_1"), group = "Sex", 
       pos = "bottomleft", units = "days", CI = F, legend = T, title = "")

```

It is also possible to plot cumulative incidence plots with function *plotci*.

## Others

An "automatic" summary of a survival object can be obtained as follows:
```{r, results='asis'}
petsum(data = lung, response = c("time","status_0_1"), group = 1,
       times=c(365,720,1095), units="days")
petsum(data = lung, response = c("time","status_0_1"), group = 'Sex',
       times=c(365,720,1095), units="days")

```

